Analysis of the King Street Traffic Pilot Project on Improving the Reliability, Speed, and Capacity of Transportation

### 2024-12-03 paper/paper.qmd
Add files via upload

---
title: "Analysis of the King Street Traffic Pilot Project on Improving the Reliability, Speed, and Capacity of Transportation"
author: 
  - liu zilin
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: "November 26, 2024"
date-format: long
abstract: "The paper provides a detailed analysis of the King Street transport pilot project, which aims to assess the impact of prioritizing trams over private cars on transport reliability, speed and capacity. Through the modeling and improvement of traffic data, the study gradually optimized the model variables and found that the model after logarithmic transformation performed best, with R-Square = 0.6345, which significantly improved the explanatory power of traffic flow changes. The pilot policy has achieved significant results in reducing traffic pressure at specific intersections and reducing interference from private cars. The effect of the policy is particularly significant on road sections with heavy traffic and during peak hours. In addition, the impact of different time periods and intersection characteristics on traffic patterns shows complex dynamic characteristics, which further indicates that targeted adjustment of traffic signals and optimization of priority policy implementation strategies will help further improve policy effects."
format: pdf
number-sections: true
bibliography: references.bib
citeproc: true
---

# Introduction

The King Street Transit Pilot is a focused project designed to assess the impact of prioritizing trams over private vehicles on key transportation metrics, including reliability, speed, and capacity. Launched on November 12, 2017, between Bathurst Street and Jarvis Street, the project represents a critical effort to address Toronto’s urban mobility challenges in its busiest transit corridor. To evaluate the pilot’s effectiveness, baseline traffic and pedestrian data were collected in October and early November 2017. The study employs advanced statistical modeling to analyze traffic flow changes, with a specific focus on identifying the impact of the transit-first policy at critical intersections and during peak hours. Through iterative modeling improvements, the study identified that a log-transformed model with provided the strongest explanatory power, highlighting the policy’s effectiveness in reducing congestion and enhancing transit efficiency.

@@

@@

This survey data is titled About King St. Transit Pilot - Traffic & Pedestrian Volumes Summary and is available on Open Data Toronto at [https://open.toronto.ca/dataset/king-st-transit-pilot-traffic-pedestrian-volumes-summary/](https://open.toronto.ca/dataset/king-st-transit-pilot-traffic-pedestrian-volumes-summary/). It can be downloaded programmatically via the API, with example R code provided in the file "00-download_data.R".This dataset pertains to the King Street Transit Pilot, which commenced on November 12, 2017, and was implemented along King Street between Bathurst Street and Jarvis Street. The pilot aimed to prioritize streetcar traffic over private vehicles to improve transit reliability, speed, and capacity. The dataset provides monthly updates on traffic and pedestrian volumes recorded within the pilot area throughout the project, offering valuable data for analyzing the impacts of this transit initiative. It serves as a critical resource for evaluating the effectiveness of the pilot in optimizing urban transit and informing future city planning and transportation policies.

@@

##  Variables and Descriptions

@@

@@

From the data set, we can find that there is a one-to-one correspondence between int_id and intersection_name, so we only need to focus on the intersection_name variable. At the same time, pedestrians, vehicles, and bicycles are also important classification variables for our subsequent data analysis. In addition, there are differences in traffic in different time periods, so period_name is also one of the key variables to consider. In summary, we analyze these three variables in detail and give their visualizations with volume respectively.

@@

The dataset contains 21 unique intersections. The different intersections and statistical numbers are shown in the following table.

@@

# get package
package <- show_package("c6a251fb-e5dc-4d9e-803a-8941501d94a3")
package

@@

The dataset contains 3 unique classifications.

@@

The dataset contains 8 unique period_names.

@@

```{r echo=FALSE,message=FALSE,warning=FALSE,results='hide'}
# Box plot: Traffic volume distribution by period_name
ggplot(data, aes(x = period_name, y = as.numeric(volume), fill = period_name)) +
  geom_boxplot(outlier.colour = "red", outlier.size = 2) +
  labs(title = "Volume Distribution by Period Name",
       x = "Period Name",
       y = "Volume") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    legend.position = "bottom",                      
    legend.title = element_text(size = 10),           
    legend.text = element_text(size = 8)              
  ) +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE))  
```

Finally, Intersection_name and Classification are combined for analysis. Through visualization, we can clearly see the detailed changes in the volume for different Classifications and different Intersection_names. It can be seen that the comparison of the volume in the pilot Bathurst and Jarvis area and other places provides an intuitive feeling for our subsequent data analysis.

# Model

@@

According to the dataset introduction, selection of important datasets, and visualization of single and interactive datasets, we hope to build a model to verify whether the pilot project launched between Bathurst Street and Jarvis Street has improved the reliability, speed and capacity of traffic. Therefore, through the last figure above, this article first builds the model as follows: classification (Pedestrians, Cyclists, Vehicles) is used as a categorical variable, and a dummy variable is generated. For the Intersection_name variable containing "Bathurst" or "Jarvis", it is used as a 1-0 variable. If the Intersection_name variable contains "Bathurst" or "Jarvis", we set it to 1, otherwise it is 0. Volume is modeled as the dependent variable, and its mathematical expression is

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 508.9107 & 47.3276 & 10.75 & 0.0000 \\ 
  classificationPedestrians & 1824.9326 & 55.8484 & 32.68 & 0.0000 \\ 
  classificationVehicles & 2126.6516 & 59.0786 & 36.00 & 0.0000 \\ 
  intersection\_binary & -709.9550 & 46.2475 & -15.35 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

After linearity, homogeneity of variance, and residual normality tests, it was found that the results were not ideal. From the visualization diagram, it can be seen intuitively that it does not meet the assumptions required by the linear model, so the model needs to be improved.

@@

In order to further improve the model, we consider adding the period_name variable. Because the volume of different time periods varies greatly, we add the period_name variable as a multi-classification variable to the original model for modeling in the improved model. Its mathematical expression is

\begin{equation}
volume=\beta_{0}+\beta_{1}Pedestrians+\beta_{2}Vehicles+\beta_{3}interaction_{binary}+\sum\limits_{k=1}^{K-1}\beta_{k+3}period_{name_k}+\epsilon
\end{equation}

In the expression, the former variable has the same interpretation as in model 1, and $period_{name_{k}}$ is a time period classification variable containing$ K$ categories, where $K$ is 8.

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 2904.2470 & 70.4428 & 41.23 & 0.0000 \\ 
  classificationPedestrians & 1828.1000 & 46.3646 & 39.43 & 0.0000 \\ 
  classificationVehicles & 2126.6516 & 49.0462 & 43.36 & 0.0000 \\ 
  intersection\_binary & -688.9816 & 38.3977 & -17.94 & 0.0000 \\ 
  period\_name24 Hour & 1309.1426 & 125.9938 & 10.39 & 0.0000 \\ 
  period\_nameAfternoon (12:00-17:00) & -2846.9106 & 78.5888 & -36.23 & 0.0000 \\ 
  period\_nameAM Peak Period (07:00-10:00) & -3056.8523 & 78.5888 & -38.90 & 0.0000 \\ 
  period\_nameEvening (17:00-22:00) & -2697.8773 & 78.5888 & -34.33 & 0.0000 \\ 
  period\_nameMidday (10:00-16:00) & -2333.5967 & 87.2579 & -26.74 & 0.0000 \\ 
  period\_nameMorning (08:00-12:00) & -2970.3300 & 78.5888 & -37.80 & 0.0000 \\ 
  period\_namePM Peak Period (16:00-19:00) & -2733.2106 & 78.5888 & -34.78 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

After linearity, homogeneity of variance, and residual normality tests, the results are still not ideal. From the visualization diagram, we can intuitively see that although it is improved compared to the first model, it still does not meet the basic assumptions required by the linear model. Therefore, the model needs to be further improved.

@@

Based on the previous two models, due to the large difference in volume, in this model, I took the logarithm of the volume value for modeling analysis. The specific mathematical expression is as follows

\begin{equation}
\log volume=\beta_{0}+\beta_{1}Pedestrians+\beta_{2}Vehicles+\beta_{3}interaction_{binary}+\sum\limits_{k=1}^{K-1}\beta_{k+3}period_{name_k}+\epsilon
\end{equation}

This expression follows the previous results, and for the dependent variable, the logarithm is taken as the dependent variable of the new model, and this model is used as the final model for modeling. The results of the modeling will be elaborated in detail in the next section.

# Results

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 5.7476 & 0.0460 & 124.84 & 0.0000 \\ 
  classificationPedestrians & 2.6326 & 0.0303 & 86.88 & 0.0000 \\ 
  classificationVehicles & 2.8213 & 0.0321 & 88.01 & 0.0000 \\ 
  intersection\_binary & -0.5716 & 0.0251 & -22.78 & 0.0000 \\ 
  period\_name24 Hour & 0.3836 & 0.0823 & 4.66 & 0.0000 \\ 
  period\_nameAfternoon (12:00-17:00) & -1.3993 & 0.0514 & -27.24 & 0.0000 \\ 
  period\_nameAM Peak Period (07:00-10:00) & -1.4924 & 0.0514 & -29.06 & 0.0000 \\ 
  period\_nameEvening (17:00-22:00) & -1.0790 & 0.0514 & -21.01 & 0.0000 \\ 
  period\_nameMidday (10:00-16:00) & -0.9272 & 0.0570 & -16.26 & 0.0000 \\ 
  period\_nameMorning (08:00-12:00) & -1.3773 & 0.0514 & -26.81 & 0.0000 \\ 
  period\_namePM Peak Period (16:00-19:00) & -1.0947 & 0.0514 & -21.31 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

@@

## Model diagnostics

```{r echo=FALSE,message=FALSE,warning=FALSE,results='hide'}
residuals <- residuals(log_model)
fitted_values <- fitted(log_model)
par(mfrow = c(2, 2))

The results of the above logarithmic model are diagnosed from the perspectives of linearity, variance homogeneity, and residual normality. From the following figure, we can easily see that for the test of linearity (the first figure), the residuals are randomly distributed on both sides of the zero line, without obvious trends or patterns, so the linearity is satisfied. For the variance homogeneity test, it can be seen that the scattered points are evenly distributed along the zero line, satisfying the variance homogeneity. For the residual normality test, the QQ plot points are close to the reference line, so the residuals are close to the normal distribution, and the assumption is satisfied. From the histogram, the residuals are centered at 0 and are symmetrically bell-shaped, so the normality test is satisfied. All tests passed, so the logarithmic model is the final model selected in this article.

@@

# Discussion

@@

The model results show that by gradually optimizing the model variables, the explanatory power is significantly improved: the basic model (Model 1,$R^2$ = 0.2051) only includes traffic classification and intersection characteristics, and has low explanatory power; the model adding time period variables (Model 2 , $R^2$ = 0.4527) and the model with logarithmic transformation of the dependent variable (Log Model, $R^2$ = 0.6345) can better reflect changes in traffic capacity. Combined with the coefficient analysis of traffic classification variables, the traffic volume contribution of vehicles (Vehicles) is significantly higher than that of cyclists and pedestrians, while the intersection characteristic variables indicate that the traffic volume of "Bathurst" and "Jarvis" is relatively low, which may be related to the pilot policy reduction Related to interference with private vehicle traffic. However, while prioritizing trams may have reduced traffic bottlenecks and improved traffic efficiency, whether the decline in private car traffic has a negative impact on overall traffic capacity requires further verification. From the perspective of the purpose of the policy, if the traffic reduction during peak periods is mainly concentrated on private cars and the tram traffic is stable or even increases, then the policy goal is basically achieved; but if the overall traffic flow drops significantly, the policy effect may need to be refined. analyze. Therefore, further hierarchical analysis of the flow trends of various transportation modes, especially the performance during peak periods, is the key to evaluating the effectiveness of policies.

@@

>>>>

---
title: "Analysis of the King Street Traffic Pilot Project on Improving the Reliability, Speed, and Capacity of Transportation"
author: 
  - Liu Zilin
thanks: "Code and data are available at: [https://github.com/zilin1017/King-Street-Traffic-Pilot-Project](https://github.com/zilin1017/King-Street-Traffic-Pilot-Project)."
date: "December 1, 2024"
date-format: long
abstract: "The paper provides a detailed analysis of the King Street transport pilot project, which aims to assess the impact of prioritizing trams over private cars on transport reliability, speed and capacity. Through the modeling and improvement of traffic data, the study gradually optimized the model variables and found that the model after logarithmic transformation performed best, with R-Square = 0.6345, which significantly improved the explanatory power of traffic flow changes. The pilot policy has achieved significant results in reducing traffic pressure at specific intersections and reducing interference from private cars. The effect of the policy is particularly significant on road sections with heavy traffic and during peak hours. In addition, the impact of different time periods and intersection characteristics on traffic patterns shows complex dynamic characteristics, which further indicates that targeted adjustment of traffic signals and optimization of priority policy implementation strategies will help further improve policy effects."
format: pdf
number-sections: true
bibliography: references.bib
citeproc: true
---
# Introduction

The King Street Transit Pilot[@king_street_pilot_2019] is a focused project designed to assess the impact of prioritizing trams over private vehicles on key transportation metrics, including reliability, speed, and capacity. Launched on November 12, 2017, between Bathurst Street and Jarvis Street, the project represents a critical effort to address Toronto’s urban mobility challenges in its busiest transit corridor. To evaluate the pilot’s effectiveness, baseline traffic and pedestrian data were collected in October and early November 2017. The study employs advanced statistical modeling to analyze traffic flow changes, with a specific focus on identifying the impact of the transit-first policy at critical intersections and during peak hours. Through iterative modeling improvements, the study identified that a log-transformed model with provided the strongest explanatory power, highlighting the policy’s effectiveness in reducing congestion and enhancing transit efficiency.

@@

The overall structure of the paper is arranged as follows. @sec-data introduces the data required for the study, including the data source, the main content of the data, descriptions of all variables, and a detailed introduction and visual analysis of the important variables required in the modeling stage. @sec-model builds a model based on the selected variables, and improves the model in turn through model diagnosis to obtain the final applicable model. The logarithm of the variable is used as the dependent variable of the regression model, and the remaining variables are used as binary variables or multi-classification variables for modeling. @sec-results explains the specific results of the final model and the comparison of the results of the three improved models. @sec-discussion the final model is diagnosed to illustrate the effectiveness of the model. In the fifth part, the article discusses and analyzes the above results, and introduces the shortcomings of the article in modeling and discussion as well as the direction for future improvement.

@@

This survey data is titled About King St. Transit Pilot - Traffic & Pedestrian Volumes Summary and is available on Open Data Toronto at [https://open.toronto.ca/dataset/king-st-transit-pilot-traffic-pedestrian-volumes-summary/](https://open.toronto.ca/dataset/king-st-transit-pilot-traffic-pedestrian-volumes-summary/). It can be downloaded programmatically via the API, with example `R` code provided in the file "00-download_data.R".This dataset pertains to the King Street Transit Pilot, which commenced on November 12, 2017[@toronto_transit_data_2017,@toronto_king_street_proposal_2017a], and was implemented along King Street between Bathurst Street and Jarvis Street. The pilot aimed to prioritize streetcar traffic over private vehicles to improve transit reliability, speed, and capacity. The dataset provides monthly updates on traffic and pedestrian volumes recorded within the pilot area throughout the project, offering valuable data for analyzing the impacts of this transit initiative. It serves as a critical resource for evaluating the effectiveness of the pilot in optimizing urban transit and informing future city planning and transportation policies.

@@

## Overview

After introducing the source and background of the data, here we will explain how to use the `R` language [@RCoreTeam] functions and some additional packages learned in the course to process the data. Here is a unified overview. The `dplyr` package [@dplyr] is a grammar of data manipulation, providing a consistent set of verbs that help us solve the most common data manipulation challenges. In this package, this article mainly uses the `mutate` function and the `filter`[@dplyrFilter] function, where the `mutate`[@dplyrMutate] function creates new columns that are functions of existing variables. The `filter` function is used to subset a data frame, retaining all rows that satisfy conditions.In the visualization stage, this article uses the `ggplot`[@ggplot2] package to draw graphics, and when analyzing the results, in order to see the output results more intuitively, this article also uses the `xtable`[@xtable] package to convert the results into `LaTex` format for output. Finally, in order to output the variable data that needs to be analyzed, this article also draws on the `arrow`[@arrowR] package recommended in the course to output data in `parquet` format.

## Measurement

First, in order to better understand the data variables, the variable names and their specific explanations are given in Table 1.

@@

After further analysis of the data set, we found that the first column, named `id`, indicates the number of data in the data set, and the second column, named `aggregation_period`, indicates the time when the data was collected. These are irrelevant to the variables required for model building, so they are no longer used in subsequent data analysis. The third column, named `intersection_name`, indicates the intersection where the data was collected. Since we are verifying Bathurst Street and Jarvis Street, we assign 1 to the intersection where one of these two streets exists in the data, otherwise 0, to construct a binary dummy variable[@wikipedia_dummy_variable]. The fourth column, named `px`, corresponds to intersection_name, so it is no longer considered again. The fifth column, named `classification`, indicates Differentiates between pedestrians, vehicles, and cyclists. It is treated as a multi-classification (3-classification) variable in the model building. The last two variables, `period_name` and `volume`, cannot be considered as a single period because `period_name` can distinguish many time periods (subsequent model improvements are also based on this). Therefore, they are considered as multi-classification variables. Finally, `volume`, a numerical data, is constructed as the dependent variable of the model. At the same time, the data can be transformed accordingly and put into the model (such as logarithmic transformation).

@@

@@

The dataset contains 21 unique intersections,as shown in Table 2. The different intersections and statistical numbers are shown in the following table.

@@

# get package
#package <- show_package("c6a251fb-e5dc-4d9e-803a-8941501d94a3")
#package

@@

The dataset contains 3 unique classifications,as shown in Table 3.

@@

The dataset contains 8 unique period_names,as shown in Table 4.

@@

```{r echo=FALSE,message=FALSE,warning=FALSE,results='hide',fig.width=8,fig.height=6}
# Box plot: Traffic volume distribution by period_name
ggplot(data, aes(x = period_name, y = as.numeric(volume), fill = period_name)) +
  geom_boxplot(outlier.colour = "red", outlier.size = 2) +
  labs(title = "Volume Distribution by Period Name",
       x = "Period Name",
       y = "Volume") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    legend.position = "bottom",                      
    legend.title = element_text(size = 10),           
    legend.text = element_text(size = 8)              
  ) +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE))  
```

# Model {#sec-model}

@@

According to the dataset introduction, selection of important datasets, and visualization of single and interactive datasets, we hope to build a model to verify whether the pilot project launched between Bathurst Street and Jarvis Street has improved the reliability, speed and capacity of traffic. Therefor, this article first builds the model as follows: classification (Pedestrians, Cyclists, Vehicles) is used as a categorical variable, and a dummy variable is generated. For the Intersection_name variable containing "Bathurst" or "Jarvis", it is used as a 1-0 variable. If the Intersection_name variable contains "Bathurst" or "Jarvis", we set it to 1, otherwise it is 0. Volume is modeled as the dependent variable, and its mathematical expression is

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 508.9107 & 47.3276 & 10.75 & 0.0000 \\ 
  classificationPedestrians & 1824.9326 & 55.8484 & 32.68 & 0.0000 \\ 
  classificationVehicles & 2126.6516 & 59.0786 & 36.00 & 0.0000 \\ 
  intersection\_binary & -709.9550 & 46.2475 & -15.35 & 0.0000 \\ 
   \hline
\end{tabular}
\caption{Modeling results of the initial model}
\end{table}

After linearity, homogeneity of variance, and residual normality tests, it was found that the results were not ideal. From the visualization diagram((Appendix B_1), it can be seen intuitively that it does not meet the assumptions required by the linear model, so the model needs to be improved.

@@

In order to further improve the model, we consider adding the period_name variable. Because the volume of different time periods varies greatly, we add the period_name variable as a multi-classification variable to the original model for modeling in the improved model. Its mathematical expression is 
\begin{equation}
volume=\beta_{0}+\beta_{1}Pedestrians+\beta_{2}Vehicles+\beta_{3}interaction_{binary}+\sum\limits_{k=1}^{K-1}\beta_{k+3}period_{name_k}+\epsilon
\end{equation}
In the expression, the former variable has the same interpretation as in model 1, and $period_{name_{k}}$ is a time period classification variable containing $K$ categories, where $K$ is 8.

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 2904.2470 & 70.4428 & 41.23 & 0.0000 \\ 
  classificationPedestrians & 1828.1000 & 46.3646 & 39.43 & 0.0000 \\ 
  classificationVehicles & 2126.6516 & 49.0462 & 43.36 & 0.0000 \\ 
  intersection\_binary & -688.9816 & 38.3977 & -17.94 & 0.0000 \\ 
  period\_name24 Hour & 1309.1426 & 125.9938 & 10.39 & 0.0000 \\ 
  period\_nameAfternoon (12:00-17:00) & -2846.9106 & 78.5888 & -36.23 & 0.0000 \\ 
  period\_nameAM Peak Period (07:00-10:00) & -3056.8523 & 78.5888 & -38.90 & 0.0000 \\ 
  period\_nameEvening (17:00-22:00) & -2697.8773 & 78.5888 & -34.33 & 0.0000 \\ 
  period\_nameMidday (10:00-16:00) & -2333.5967 & 87.2579 & -26.74 & 0.0000 \\ 
  period\_nameMorning (08:00-12:00) & -2970.3300 & 78.5888 & -37.80 & 0.0000 \\ 
  period\_namePM Peak Period (16:00-19:00) & -2733.2106 & 78.5888 & -34.78 & 0.0000 \\ 
   \hline
\end{tabular}
\caption{Improved model building results}
\end{table}

After linearity, homogeneity of variance, and residual normality tests, the results are still not ideal. From the visualization diagram(Appendix B_2), we can intuitively see that although it is improved compared to the first model, it still does not meet the basic assumptions required by the linear model. Therefore, the model needs to be further improved.

@@

Based on the previous two models, due to the large difference in volume, in this model, I took the logarithm of the volume value for modeling analysis. The specific mathematical expression is as follows
\begin{equation}
\log volume=\beta_{0}+\beta_{1}Pedestrians+\beta_{2}Vehicles+\beta_{3}interaction_{binary}+\sum\limits_{k=1}^{K-1}\beta_{k+3}period_{name_k}+\epsilon
\end{equation}
This expression follows the previous results, and for the dependent variable, the logarithm is taken as the dependent variable of the new model, and this model is used as the final model for modeling. The results of the modeling will be elaborated in detail in the next section.

# Results {#sec-results}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 5.7476 & 0.0460 & 124.84 & 0.0000 \\ 
  classificationPedestrians & 2.6326 & 0.0303 & 86.88 & 0.0000 \\ 
  classificationVehicles & 2.8213 & 0.0321 & 88.01 & 0.0000 \\ 
  intersection\_binary & -0.5716 & 0.0251 & -22.78 & 0.0000 \\ 
  period\_name24 Hour & 0.3836 & 0.0823 & 4.66 & 0.0000 \\ 
  period\_nameAfternoon (12:00-17:00) & -1.3993 & 0.0514 & -27.24 & 0.0000 \\ 
  period\_nameAM Peak Period (07:00-10:00) & -1.4924 & 0.0514 & -29.06 & 0.0000 \\ 
  period\_nameEvening (17:00-22:00) & -1.0790 & 0.0514 & -21.01 & 0.0000 \\ 
  period\_nameMidday (10:00-16:00) & -0.9272 & 0.0570 & -16.26 & 0.0000 \\ 
  period\_nameMorning (08:00-12:00) & -1.3773 & 0.0514 & -26.81 & 0.0000 \\ 
  period\_namePM Peak Period (16:00-19:00) & -1.0947 & 0.0514 & -21.31 & 0.0000 \\ 
   \hline
\end{tabular}
\caption{Final modeling results}
\end{table}

@@

The results of the above logarithmic model are diagnosed from the perspectives of linearity, variance homogeneity, and residual normality. From the following figure(Appendix B_3), we can easily see that for the test of linearity (the first figure), the residuals are randomly distributed on both sides of the zero line, without obvious trends or patterns, so the linearity is satisfied. For the variance homogeneity test, it can be seen that the scattered points are evenly distributed along the zero line, satisfying the variance homogeneity. For the residual normality test, the QQ plot points are close to the reference line, so the residuals are close to the normal distribution, and the assumption is satisfied. From the histogram, the residuals are centered at 0 and are symmetrically bell-shaped, so the normality test is satisfied. All tests passed, so the logarithmic model is the final model selected in this article.

@@

# Discussion {#sec-discussion}

@@

The model results show that by gradually optimizing the model variables, the explanatory power is significantly improved: the basic model (Model 1,$R^2$ = 0.2051) only includes traffic classification and intersection characteristics, and has low explanatory power; the model adding time period variables (Model 2 , $R^2$ = 0.4527) and the model with logarithmic transformation of the dependent variable (Log Model, $R^2$ = 0.6345) can better reflect changes in traffic capacity. Combined with the coefficient analysis of traffic classification variables, the traffic volume contribution of vehicles (Vehicles) is significantly higher than that of cyclists and pedestrians, while the intersection characteristic variables indicate that the traffic volume of "Bathurst" and "Jarvis" is relatively low, which may be related to the pilot policy reduction Related to interference with private vehicle traffic. However, while prioritizing trams may have reduced traffic bottlenecks and improved traffic efficiency, whether the decline in private car traffic has a negative impact on overall traffic capacity requires further verification. From the perspective of the purpose of the policy, if the traffic reduction during peak periods is mainly concentrated on private cars and the tram traffic is stable or even increases, then the policy goal is basically achieved; but if the overall traffic flow drops significantly, the policy effect may need to be refined. analyze. Therefore, further hierarchical analysis of the flow trends of various transportation modes, especially the performance during peak periods, is the key to evaluating the effectiveness of policies.[@higgins2024modelling]

@@

\newpage

# Appendix

## Appendix A Interaction analysis of data

Intersection_name and Classification are combined for analysis. Through visualization, we can clearly see the detailed changes in the volume for different Classifications and different Intersection_names. It can be seen that the comparison of the volume in the pilot Bathurst and Jarvis area.This visualization is similar to the modeling result above, which is due to the negative coefficient of the variable `intersection_binary`.

## Appendix B Model diagnostics visualization results

### Initial Model Model Diagnostics

Appendix B_1:Judging from the model diagnostic results, the linear model assumptions do not seem to be met.

par(mfrow = c(1, 1)) 
```
### Improved model diagnostics

Appendix B_2:Judging from the model diagnostic results, the linear model assumptions also do not seem to be met.

### Final Model Model Diagnostics
Appendix B_3:Judging from the model diagnosis results, the linear model assumptions can basically be met.
```{r echo=FALSE,message=FALSE,warning=FALSE,results='hide'}
residuals <- residuals(log_model)
fitted_values <- fitted(log_model)
par(mfrow = c(2, 2))

par(mfrow = c(1, 1))  
```
\newpage
# References
